Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-06-27 assets/tikz/gtx_eccentricity_tikz.tex
change the example graph to add color on its edges

\documentclass[svgnames,11pt,tikz]{standalone}
\input{preambule}
\begin{document}
\tikzstyle{star}=[circle,DodgerBlue,very thick,fill opacity=.2]
\tikzstyle{star-label}=[opacity=1, , font=\Large]
\tikzstyle{removed}=[Gray,line width=1.15pt]
\begin{tikzpicture}[auto,vertex/.append style={minimum width=8mm}]
  \draw[star,Orange] (2.260, -1.063) circle [radius=4.4]  node[star-label,font=\LARGE,xshift=-10, yshift=110] {$S_1^2$};
  \draw[star,Orange] (6.504, -9.728) circle [radius=4.4]  node[star-label,font=\LARGE,xshift=-10, yshift=110] {$S_2^2$};
  \draw[star,Orange] (11.641, 1.189) circle [radius=4.4]  node[star-label,font=\LARGE,xshift=-10, yshift=110] {$S_3^2$};

  \draw[star] (0.000, -0.000) circle [radius=1.8]  node[star-label,xshift=-30, yshift=25] {$S_1^1$};
  \draw[star] (1.689, -3.448) circle [radius=1.8]  node[star-label,xshift=-30, yshift=5] {$S_2^1$};
  \draw[star] (3.734, 0.896) circle [radius=1.8]  node[star-label,xshift=-30, yshift=5] {$S_3^1$};
  \draw[star] (4.245, -8.664) circle [radius=1.8]  node[star-label,xshift=-22, yshift=-25] {$S_4^1$};
  \draw[star] (5.934, -12.113) circle [radius=1.8]  node[star-label,xshift=-15, yshift=35] {$S_5^1$};
  \draw[star] (7.978, -7.768) circle [radius=1.8]  node[star-label,xshift=30, yshift=25] {$S_6^1$};
  \draw[star] (9.381, 2.252) circle [radius=1.8]  node[star-label,xshift=-15, yshift=30] {$S_7^1$};
  \draw[star] (11.071, -1.196) circle [radius=1.8]  node[star-label,xshift=-30, yshift=25] {$S_8^1$};
  \draw[star] (13.115, 3.149) circle [radius=1.8]  node[star-label,xshift=-30, yshift=20	] {$S_9^1$};

@@

  \draw[edge] (n1) edge [bend left =0] node[] {} (n2);
  \draw[edge] (n1) edge [bend left =0] node[] {} (n3);
  \draw[edge] (n1) edge [bend left =0] node[] {} (n4);
  \draw[edge] (n1) edge [bend left =0] node[] {} (n5);
  \draw[edge] (n2) edge [bend left =25] node[] {} (n6);
  \draw[edge,removed] (n2) edge [bend left =0] node[] {} (n9);
  \draw[edge,removed] (n3) edge [bend left =-20] node[] {} (n12);
  \draw[edge] (n4) edge [bend left =20] node[] {} (n14);
  % \draw[edge] (n3) edge [bend left =-20] node[] {} (n18);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n7);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n8);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n9);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n10);
  % \draw[edge] (n7) edge [bend left =-15] node[] {} (n43);
  % \draw[edge] (n9) edge [bend left =-10] node[] {} (n32);
  \draw[edge] (n8) .. controls ++(-40:3) and ++(240: 2) .. (n37);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n12);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n13);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n14);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n15);
  \draw[edge,removed] (n13) edge [bend left =0] node[] {} (n29);
  % \draw[edge] (n12) edge [bend left =0] node[] {} (n18);
  \draw[edge] (n15) .. controls ++(-40:3) and ++(64: 3.5) .. (n26);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n17);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n18);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n19);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n20);
  \draw[edge] (n17) edge [bend left =0] node[] {} (n23);
  %\draw[edge] (n19) edge [bend left =0] node[] {} (n27);
  \draw[edge] (n19) edge [bend left =0] node[] {} (n29);
  \draw[edge,removed] (n20) edge [bend left =0] node[] {} (n24);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n22);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n23);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n24);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n25);
  \draw[edge,removed] (n25) edge [bend left =-20] node[] {} (n42);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n27);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n28);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n29);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n30);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n32);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n33);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n34);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n35);
  \draw[edge] (n32) edge [bend left =0] node[] {} (n39);
  \draw[edge] (n35) edge [bend left =0] node[] {} (n43);
  \draw[edge,removed] (n33) edge [bend left =-25] node[] {} (n38);
  \draw[edge,removed] (n34) edge [bend left =20] node[] {} (n43);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n37);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n38);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n39);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n40);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n42);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n43);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n44);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n45);

  \draw[Green, line width=2pt] (11.8, 6.5) 
  .. controls ++(190:1) and ++(55: 2) .. (-2, 2.5)
  .. controls  ++(55: -4) and ++(170:4) .. (6, -15) 
  .. controls  ++(-10:9) and ++(10:9) .. node[pos=.4,font=\Huge,xshift=-15pt] {$S_1^3$} cycle ;
\end{tikzpicture}
\end{document}

>>>>

\documentclass[svgnames,11pt,tikz]{standalone}
\input{preambule}
\begin{document}
\tikzstyle{star}=[DodgerBlue,line width=2pt]
\tikzstyle{star-label}=[font=\Large]
\tikzstyle{removed}=[dashed,line width=1.7pt]
\begin{tikzpicture}[auto,vertex/.append style={minimum width=8mm},
  edge/.append style={line width=2.2pt,color=DodgerBlue!90!Black}]
  \draw[star,Orange] (2.260, -1.063) circle [radius=4.4]  node[star-label,font=\LARGE,xshift=-10, yshift=110] {$\mathbf{S_1^2}$};
  \draw[star,Orange] (6.504, -9.728) circle [radius=4.4]  node[star-label,font=\LARGE,xshift=-10, yshift=110] {$\mathbf{S_2^2}$};
  \draw[star,Orange] (11.641, 1.189) circle [radius=4.4]  node[star-label,font=\LARGE,xshift=-10, yshift=110] {$\mathbf{S_3^2}$};

  \draw[star] (0.000, -0.000) circle [radius=1.8]  node[star-label,xshift=-30, yshift=25] {$\mathbf{S_1^1}$};
  \draw[star] (1.689, -3.448) circle [radius=1.8]  node[star-label,xshift=-30, yshift=5] {$\mathbf{S_2^1}$};
  \draw[star] (3.734, 0.896) circle [radius=1.8]  node[star-label,xshift=-30, yshift=5] {$\mathbf{S_3^1}$};
  \draw[star] (4.245, -8.664) circle [radius=1.8]  node[star-label,xshift=-22, yshift=-25] {$\mathbf{S_4^1}$};
  \draw[star] (5.934, -12.113) circle [radius=1.8]  node[star-label,xshift=-15, yshift=35] {$\mathbf{S_5^1}$};
  \draw[star] (7.978, -7.768) circle [radius=1.8]  node[star-label,xshift=30, yshift=25] {$\mathbf{S_6^1}$};
  \draw[star] (9.381, 2.252) circle [radius=1.8]  node[star-label,xshift=-15, yshift=30] {$\mathbf{S_7^1}$};
  \draw[star] (11.071, -1.196) circle [radius=1.8]  node[star-label,xshift=-30, yshift=25] {$\mathbf{S_8^1}$};
  \draw[star] (13.115, 3.149) circle [radius=1.8]  node[star-label,xshift=-30, yshift=20	] {$\mathbf{S_9^1}$};

@@

  \draw[edge] (n1) edge [bend left =0] node[] {} (n2);
  \draw[edge] (n1) edge [bend left =0] node[] {} (n3);
  \draw[edge] (n1) edge [bend left =0] node[] {} (n4);
  \draw[edge] (n1) edge [bend left =0] node[] {} (n5);
  \draw[edge,Orange!90!Black] (n2) edge [bend left =25] node[] {} (n6);
  \draw[edge,removed,Orange!90!Black] (n2) edge [bend left =0] node[] {} (n9);
  \draw[edge,removed,Orange!90!Black] (n3) edge [bend left =-20] node[] {} (n12);
  \draw[edge,Orange!90!Black] (n4) edge [bend left =20] node[] {} (n14);
  % \draw[edge] (n3) edge [bend left =-20] node[] {} (n18);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n7);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n8);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n9);
  \draw[edge] (n6) edge [bend left =0] node[] {} (n10);
  % \draw[edge] (n7) edge [bend left =-15] node[] {} (n43);
  % \draw[edge] (n9) edge [bend left =-10] node[] {} (n32);
  \draw[edge,Green!90!Black] (n8) .. controls ++(-40:3) and ++(240: 2) .. (n37);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n12);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n13);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n14);
  \draw[edge] (n11) edge [bend left =0] node[] {} (n15);
  \draw[edge,removed,Green!90!Black] (n13) edge [bend left =0] node[] {} (n29);
  % \draw[edge] (n12) edge [bend left =0] node[] {} (n18);
  \draw[edge,Green!90!Black] (n15) .. controls ++(-40:3) and ++(64: 3.5) .. (n26);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n17);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n18);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n19);
  \draw[edge] (n16) edge [bend left =0] node[] {} (n20);
  \draw[edge,Orange!90!Black] (n17) edge [bend left =0] node[] {} (n23);
  %\draw[edge] (n19) edge [bend left =0] node[] {} (n27);
  \draw[edge,Orange!90!Black] (n19) edge [bend left =0] node[] {} (n29);
  \draw[edge,removed,Orange!90!Black] (n20) edge [bend left =0] node[] {} (n24);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n22);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n23);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n24);
  \draw[edge] (n21) edge [bend left =0] node[] {} (n25);
  \draw[edge,removed,Green!90!Black] (n25) edge [bend left =-20] node[] {} (n42);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n27);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n28);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n29);
  \draw[edge] (n26) edge [bend left =0] node[] {} (n30);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n32);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n33);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n34);
  \draw[edge] (n31) edge [bend left =0] node[] {} (n35);
  \draw[edge,Orange!90!Black] (n32) edge [bend left =0] node[] {} (n39);
  \draw[edge,Orange!90!Black] (n35) edge [bend left =0] node[] {} (n43);
  \draw[edge,removed,Orange!90!Black] (n33) edge [bend left =-25] node[] {} (n38);
  \draw[edge,removed,Orange!90!Black] (n34) edge [bend left =20] node[] {} (n43);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n37);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n38);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n39);
  \draw[edge] (n36) edge [bend left =0] node[] {} (n40);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n42);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n43);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n44);
  \draw[edge] (n41) edge [bend left =0] node[] {} (n45);

  \draw[star, Green!90!Black] (11.8, 6.5) 
  .. controls ++(190:1) and ++(55: 2) .. (-2, 2.5)
  .. controls  ++(55: -4) and ++(170:4) .. (6, -15) 
  .. controls  ++(-10:9) and ++(10:9) .. node[pos=.4,font=\Huge,xshift=-15pt] {$\mathbf{S_1^3}$} cycle ;
\end{tikzpicture}
\end{document}

### 2017-06-27 gtx_algorithm.tex
change the example graph to add color on its edges

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.78\linewidth]{tikz/gtx_eccentricity_tikz.pdf}
  \caption[The hierarchical structure of stars created by \gtx{}]{%
    The execution of the \gtx{} algorithm. The original graph is made of the solid edges
    connecting the nodes labeled by  their index. Edges forming the final spanning tree are in black
    while the others are in gray. The four shades of gray, from white to dark gray
    denote increasing node eccentricity (as computed at the end of the algorithm). The \ith{} star
    created during the \jth{} iteration of the algorithm is denoted $S_i^j$. Refer to the main text
    for the complete description of the execution.}
  \label{fig:gtx_eccentricity}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.78\linewidth]{tikz/gtx_eccentricity_tikz.pdf}
  \caption[The hierarchical structure of stars created by \gtx{}]{%
    The execution of the \gtx{} algorithm. The original graph is made of the solid and dashed edges
    connecting the nodes labeled by their index. Edges forming the final spanning tree are solid
    while the others are dashed. Their colors indicate at which iteration they were chosen to be inside a
    star. The four shades of gray, from white to dark gray
    denote increasing node eccentricity (as computed at the end of the algorithm). The \ith{} star
    created during the \jth{} iteration of the algorithm is denoted $S_i^j$. Refer to the main text
    for the complete description of the execution.}
  \label{fig:gtx_eccentricity}
\end{figure}
